\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-05-30 graph_abs.tex
.

@@

>>>>

In this section, we present the model of the hybrid dynamical system
under test, and the background for PWA relational abstractions.

\mypara{System under test ($\System$)}

We assume that $\System$ is a hybrid dynamical system with exogenous
inputs modeling an embedded control system. The system state-space
(denoted $\HybridStates$) is a subset of $\Modes \times \Reals^n$,
where $\Modes$ is a finite set of discrete modes, and $\Reals^n$
represents the continuous-valued state-space. For ease of exposition,
we assume that the hybrid system is effectively a switched-mode
dynamical system, \ie, the mode of the system is completely determined
by its state.  An input to $\System$ is assumed to be a time-bounded
{\em signal}, \ie, a function from $[0,T]$ to $\Inputs$, with $T$ as
the time horizon, and $\Inputs \subseteq \Reals^k$.  In this paper, we
view $\System$ as effectively black-box equipped with a forward
simulation map, in a simulation time-step of $\Delta_t$ from time $t$,
allows computing the unique reachable state $\vx \in \HybridStates$
given state-input pair $(\vx,\vu)$.

% time and input parameterized reachability relation $\reach{t,
% \vu}_\System \subseteq \HybridStates \times \HybridStates$ as follows:
% $\simulate^{\System}:
% (\vx, \vu, t) \mapsto \vx$, where $\vx \in \HybridStates$, $\vu \in
% \Inputs$ and $t \in [0,T]$.

% Given the hybrid state space $\vx\in\HybridStates$ and input space $u
% \in\Inputs$ and time step $t$, it computes the unique successor state
% $\vy=\simulate^{\System}(\vx,u,t)$ such that $\vx \reach{t,u} \vy$.

\begin{definition}[System Evolution]
    The behavior of system $\System$ at time $t$ is described as an
    evolution in the hybrid state-space $\HybridStates$ under the
    effect of the input $\vu \in \Inputs$ at time $t$. The forward
    simulation map $\simulate^\System : \HybridStates \times \Inputs
    \times \Reals^+ \mapsto \HybridStates$, maps a state $\x$ at time
    $t$ to a new state $\x'$ at time $t+\Delta_t$, under a constant
    input $\vu$.  Finally, we define the time and input parameterized
    reachability relation $\reach{t,u} \subseteq \HybridStates \times
    \HybridStates$ such that $(\vx,\vx') \in \reach{t,u}$ iff
    $\vx'=\simulate^{\System}(\vx,u,t)$.
\end{definition}

\mypara{System Assumptions:} We require that $\System$ can always be
simulated forward in time with deterministic results. This in turn
requires existence and uniqueness of trajectories over a finite time
horizon $[0,T]$, which can be guaranteed by Lipschitz continuity of
the vector field in each underlying hybrid mode, ruling away issues
such as finite escape times~\cite{Meiss/2007/Differential}, and having
well-defined semantics for simulations at switching boundaries. While
these assumptions hold for the dynamical system examples which we
consider in this paper, such assumptions can be restrictive for
general control system models. When analyzing a system that does not
obey theoretical conditions that allow deterministic simulation, we
assume that the underlying tool used for numerical approximations of
system behaviors uses deterministic simulation semantics.  Finally, we
assume full observability of the system state, validate our results
only against the $\simulate$ function (as the analytic closed-form
representation of the system dynamics is assumed to be unavailable).
From here on, we drop the subscript $\System$ whenever it is clear
from the context. Also, to ease the presentation, we conflate the
inputs with the state and denote them by $\vx$.

% Abstractions for black box systems
% graph based
% enrichment procedure

@@

\todo{Add figure? graph-abs -enrich-> pwa-transition-system -bmc->
concrete-CEX}

### 2017-05-30 prelims.tex
.

In this section, we present the model of the hybrid dynamical system
under test, and the background for PWA relational abstractions.

\mypara{System under test ($\System$)}

We assume that $\System$ is a hybrid dynamical system with exogenous
inputs modeling an embedded control system. The system state-space
(denoted $\HybridStates$) is a subset of $\Modes \times \Reals^n$,
where $\Modes$ is a finite set of discrete modes, and $\Reals^n$
represents the continuous-valued state-space. For ease of exposition,
we assume that the hybrid system is effectively a switched-mode
dynamical system, \ie, the mode of the system is completely determined
by its state.  An input to $\System$ is assumed to be a time-bounded
{\em signal}, \ie, a function from $[0,T]$ to $\Inputs$, with $T$ as
the time horizon, and $\Inputs \subseteq \Reals^k$.  In this paper, we
view $\System$ as effectively black-box equipped with a forward
simulation map, in a simulation time-step of $\Delta_t$ from time $t$,
allows computing the unique reachable state $\vx \in \HybridStates$
given state-input pair $(\vx,\vu)$.

% time and input parameterized reachability relation $\reach{t,
% \vu}_\System \subseteq \HybridStates \times \HybridStates$ as follows:
% $\simulate^{\System}:
% (\vx, \vu, t) \mapsto \vx$, where $\vx \in \HybridStates$, $\vu \in
% \Inputs$ and $t \in [0,T]$.

% Given the hybrid state space $\vx\in\HybridStates$ and input space $u
% \in\Inputs$ and time step $t$, it computes the unique successor state
% $\vy=\simulate^{\System}(\vx,u,t)$ such that $\vx \reach{t,u} \vy$.

\begin{definition}[System Evolution]
    The behavior of system $\System$ at time $t$ is described as an
    evolution in the hybrid state-space $\HybridStates$ under the
    effect of the input $\vu \in \Inputs$ at time $t$. The forward
    simulation map $\simulate^\System : \HybridStates \times \Inputs
    \times \Reals^+ \mapsto \HybridStates$, maps a state $\x$ at time
    $t$ to a new state $\x'$ at time $t+\Delta_t$, under a constant
    input $\vu$.  Finally, we define the time and input parameterized
    reachability relation $\reach{t,u} \subseteq \HybridStates \times
    \HybridStates$ such that $(\vx,\vx') \in \reach{t,u}$ iff
    $\vx'=\simulate^{\System}(\vx,u,t)$.
\end{definition}

\mypara{System Assumptions:} We require that $\System$ can always be
simulated forward in time with deterministic results. This in turn
requires existence and uniqueness of trajectories over a finite time
horizon $[0,T]$, which can be guaranteed by Lipschitz continuity of
the vector field in each underlying hybrid mode, ruling away issues
such as finite escape times~\cite{Meiss/2007/Differential}, and having
well-defined semantics for simulations at switching boundaries. While
these assumptions hold for the dynamical system examples which we
consider in this paper, such assumptions can be restrictive for
general control system models. When analyzing a system that does not
obey theoretical conditions that allow deterministic simulation, we
assume that the underlying tool used for numerical approximations of
system behaviors uses deterministic simulation semantics.  Finally, we
assume full observability of the system state, validate our results
only against the $\simulate$ function (as the analytic closed-form
representation of the system dynamics is assumed to be unavailable).
From here on, we drop the subscript $\System$ whenever it is clear
from the context. Also, to ease the presentation, we conflate the
inputs with the state and denote them by $\vx$.

\subsection{Learning Dynamics using Simple Linear Regression}

@@

>>>>

@@

\section{Learning Dynamics using Simple Linear Regression}
